The {TestIdeals} package for \emph{Macaulay2}

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed some bad breaks.

\subsection*{Acknowledgements}
The authors thank other contributors of the \texttt{TestIdeals.m2} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
This paper, and the finishing touches to the \texttt{TestIdeals.m2} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.

>>>>

\subsection*{Acknowledgements}
The authors thank other contributors of the \texttt{TestIdeals.m2} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
This paper, and the finishing touches to the package \texttt{TestIdeals.m2}, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
